Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels

### 2019-04-15 report/article.tex
A report based on communication work

\documentclass[sigconf]{acmart}

%%%
%%% \BibTeX command to typeset BibTeX logo in the docs
%%\AtBeginDocument{%
%% \providecommand\BibTeX{{%
%% \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\copyrightyear{2019}
\acmYear{2019}
\setcopyright{acmlicensed}
\acmConference[ICPP '19]{ICPP 2019: 48th International Conference on Parallel Processing}{August 05--08, 2019}{Kyoto, Japan}
%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
%%\acmPrice{15.00}
%%\acmDOI{10.1145/1122445.1122456}
%%\acmISBN{978-1-4503-9999-9/18/06}

\usepackage{graphicx}

\usepackage[utf8]{inputenc}
%%\usepackage{amsmath}
%%\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{threeparttable}
\usepackage{graphicx}
\usepackage{color}
\usepackage{paralist}
\usepackage{framed}
\usepackage{caption}
%%\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{todonotes}
\usepackage{subfig}
\usepackage{multirow}

@@

%%\newcommand{\scomm}{\ensuremath{{\cal S}_{\text{COMM}}}}
%%\newcommand{\scomp}{\ensuremath{{\cal S}_{\text{COMP}}}}

\newcommand{\scomm}{\ensuremath{{S}_{\text{COMM}}}}
\newcommand{\scomp}{\ensuremath{{S}_{\text{COMP}}}}
\newcommand{\threepart}{\textsc{3Par}\xspace}

@@

\begin{document}

	\title{Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels}

	\author{Suraj Kumar}
	\affiliation{%
		\institution{Pacific Northwest National Laboratory}
		\city{Richland, Washington, USA}}
	\email{suraj.kumar@pnnl.gov}

	\author{Lionel Eyraud-Dubois}
	\affiliation{\institution{Inria Bordeaux -- Sud-Ouest}\institution{Université de Bordeaux, France}}
	\email{lionel.eyraud-dubois@inria.fr}

	\author{Sriram Krishnamoorthy}
	\affiliation{
		\institution{Pacific Northwest National Laboratory}
		\city{Richland, Washington, USA}}
	\email{sriram@pnnl.gov}

	\renewcommand{\shortauthors}{Kumar and Eyraud-Dubois, et al.}

	%
	% The abstract is a short summary of the work to be presented in the article.
	\begin{abstract}
		\todo[inline]{Initial submission deadline: April 15}
		With increasing complexity of hardwares, systems with different memory nodes are ubiquitous in High Performance Computing (HPC). It is paramount to develop strategies to overlap the data transfers between memory nodes with computations in order to exploit the full potential of these systems. In this paper, we consider the problem of deciding the order of data transfers between two memory nodes for a set of independent tasks with the objective to minimize the makespan. We prove that with limited memory capacity, obtaining the optimal order of data transfers is a NP-complete problem. We propose several heuristics for this problem and provide details about their favorable situations. We present an analysis of our heuristics on traces, obtained by running 2 molecular chemistry kernels, namely, Hartree–Fock (HF) and Coupled Cluster Single Double (CCSD) on 10 nodes of an HPC system. Our results show that some of our heuristics achieve significant overlap for moderate memory capacities and are very close to the lower bound of makespan.
	\end{abstract}

	%%\begin{CCSXML}
	%%	<ccs2012>
	%%	<concept>
	%%	<concept_id>10010520.10010553.10010562</concept_id>
	%%	<concept_desc>Computer systems organization~Embedded systems</concept_desc>
	%%	<concept_significance>500</concept_significance>
	%%	</concept>
	%%	<concept>
	%%	<concept_id>10010520.10010575.10010755</concept_id>
	%%	<concept_desc>Computer systems organization~Redundancy</concept_desc>
	%%	<concept_significance>300</concept_significance>
	%%	</concept>
	%%	<concept>
	%%	<concept_id>10010520.10010553.10010554</concept_id>
	%%	<concept_desc>Computer systems organization~Robotics</concept_desc>
	%%	<concept_significance>100</concept_significance>
	%%	</concept>
	%%	<concept>
	%%	<concept_id>10003033.10003083.10003095</concept_id>
	%%	<concept_desc>Networks~Network reliability</concept_desc>
	%%	<concept_significance>100</concept_significance>
	%%	</concept>
	%%	</ccs2012>
	%%\end{CCSXML}
	\ccsdesc[100]{Computer systems organization~ High Performance Computing }
	\ccsdesc[100]{Computing Methodologies~Modeling and Simulation}
	\ccsdesc[100]{General ~ Performance}

	\keywords{Communication Scheduling, Memory Nodes, Runtime Systems, Communication-Computation Overlap, Molecular Chemistry}

	\maketitle

@@

	Certain applications such as dense linear algebra kernels have regular structure. Therefore, it is possible to associate priorities to computations, based on the task graph structure, and to use them at runtime to make the execution efficient. In irregular applications, programmers do not know the precise structure of the task graphs in advance: tasks are added recursively based on certain sentinel constraints. For such applications, the runtime system sees a set of independent tasks and schedules them on different processing units. It is extremely important for runtimes to decide the order of data transfers for these scheduled computations so as to maximize the overlap between computations and communications. This is the main topic of this paper. We prove that the order of communications on two memory nodes with the objective of minimizing the makespan is a NP-Complete problem if the memory of the target node is limited. Our proof is inspired from work by~\cite{Papadimitriou:1980:FSL:322203.322213}, which applies a similar technique for 2-machine flowshop problem with bounded capacity. The main difference between both approaches is that they consider all tasks have the same occupation on the second machine and the memory occupation starts when the processing finishes on the first machine. On the contrary, our approach is designed for tasks appearing in scientific workloads whose memory requirements are highly irregular and we consider that memory is acquired before starting the data transfer on the communication resource. We propose different runtime strategies in order to maximize the overlap of computations and communications. We evaluate our strategies on the context of a cluster of homogeneous nodes. However, our approach is generic and easily adaptable to any system which operates on different memory spaces. Here are the important contributions of this paper:

@@

	The outline of the paper is the following. Section~\ref{sec:relatedWork} describes past work on the computations with limited memory and similar problems in the literature. In section~\ref{sec:theoreticalProof}, we present an algorithm to obtain the order of data transfers when there is not any memory capacity restriction. Then, we also prove that in general data transfer problem is NP-complete. In Section~\ref{sec:heuristics}, we propose several heuristics and describe their favorable scenarios. We mainly consider three categories of heuristics: static heuristics, dynamic heuristics and static heuristics with dynamic corrections. Sections~\ref{sec:expSetting} describes our experimental setup and we evaluate our proposed strategies on two molecular chemistry kernels in Section~\ref{sec:expResults}. Our results show that static heuristics with dynamic corrections achieve good performance in most cases. We finally propose conclusions and perspectives in Section~\ref{sec:conclusion}.

@@

	The problem considered in this paper also can be viewed as a flow shop problem: the communication link can be seen as a processing resource, and each task needs to first be handled by the communication link and then by the computational resource. Communication and computation times of a task can thus be considered as processing times on different machines. Johnson has provided scheduling strategies for 2 and 3-machine flow shop problems with infinite memory capacity~\cite{johnson}. 2-machine flow shop problem with finite buffer has been proven NP-Complete by Papadimitriou et. al~\cite{Papadimitriou:1980:FSL:322203.322213}, in which a constraint is imposed on the number of tasks that can await execution on the second machine.

@@

	%	\todo[inline]{theoretical/performance work on molecular chemistry kernels}

@@

	\noindent\textbf{Problem $DT$} : A set of tasks $ST=\{T_1,
	\cdots, T_n\}$ is scheduled on a processing unit $P$ with
	memory unit $M$ of capacity $C$. Input data for tasks of $ST$
	reside on another memory unit $M'$. $COMM_i$ is the communication time to
	transfer input data from $M'$ to $M$ for task $i$ and $COMP_i$
	is the computation time of task $i$ on $P$. We assume that these
	tasks do not produce any output data. There can be only one
	communication at a time, and $P$ can only process one task at
	a time. A task uses an amount of memory in  $M$ from the
	start of its communication to the end of its computation.

@@

	Given a schedule, \scomm($i$) and \scomp($i$) represent the
	start times of task $i$ on communication and computation
	resources. A schedule is feasible if for every time $t$, the
	amount of memory required by all tasks such that $\scomm(i) \leq t
	\leq \scomp(i) + COMP_i$ is not more than the memory capacity
	$C$. 
	For simplicity, we assume throughout the paper that tasks
	require memory only to store their input data, and thus that
	the amount of memory required by a task is proportional to its
	communication time. Without loss of generality, we consider in
	all examples of Sections~\ref{sec:theoreticalProof}
	and~\ref{sec:heuristics} that the memory requirement of a task
	is equal to its communication time.

	%% We assume through out the paper that communication time of a task is proportional to memory required by it, and follow conventional \textit{Comm Time = Latency + (Comm Volume)/Bandwidth} model.
	%%	
	We call a task $i$ compute intensive if $COMP_i \ge COMM_i$, and
	communication intensive otherwise.

@@

	\begin{algorithm}
		\caption{\label{alg:OrderOfExecutionInfinteMemory}Johnson's~\cite{johnson} algorithm (infinite memory case).}
		\begin{algorithmic}[1]
			\STATE Divide ready tasks in two sets $S_1$ and $S_2$. If computation time of a task $T$ is not less than its communication time, then $T$ is in $S_1$ otherwise in $S_2$.
			\STATE Sort $S_1$ in queue $Q$ by non-decreasing communication times
			\STATE Sort $S_2$ in queue $Q'$ by non-increasing computation times
			\STATE Append $Q'$ to $Q$
			\STATE $\tau_{\text{COMM}} \gets 0$ \hfill\COMMENT{Available time of communication resource}
			\STATE $\tau_{\text{COMP}} \gets 0$\hfill \COMMENT{Available time of computation resource}
			\WHILE{$Q \neq \emptyset$}
			\STATE Remove a task $T$ from beginning of $Q$ for processing
			\STATE $\scomm(T) \gets \tau_{\text{COMM}}$
			\STATE $\scomp(T) \gets max(\scomm(T) + COMM_T, \tau_{\text{COMP}})$
			\STATE $\tau_{\text{COMM}} \gets \scomm(T) + COMM_T$
			\STATE $\tau_{\text{COMP}} \gets \scomp(T) + COMP_T$
			\ENDWHILE
		\end{algorithmic}
	\end{algorithm}

	We also prove optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} differently in an extended version(cite).
	\subsection{Finite Memory}

@@

		\todo[inline]{SKumar: I understand that proving for an instance with memory requirement = communication time, also proves that, in general, DT problem is NP-hard. I was thinking we can directly prove the general version by adding a single line saying what to change.  I am not sure whether it is good to explicitly mention how to prove the general version. I added a line below. Feel free to remove it.}
		As mentioned previously, we consider memory requirement of a task is equal to its communication time. If it is not the case, we can adjust $C$ such that at any point in a schedule at max one $K_i$ and three $A_i$ tasks can be active.

@@

	This theorem shows that adding a memory constraint to our
	problem makes it more difficult. One additional difficulty
	compared to limited capacity 2-machine
	flowshop~\cite{Papadimitriou:1980:FSL:322203.322213}  \todo{I think you mean: infinite memory capacity 2-machine flowshop~\cite{johnson}} is that
	it may not be optimal to consider the same ordering on both
	machines:

@@

	%%\begin{figure}[htb]
	%%	
	%%	\includegraphics[scale=0.05]{Figs/staticOrderSchedules}
	%%			\caption{Task set and schedules where orders are precomputed based on different heuristics.}
	%%	\label{fig:staticOrderExample}
	%%\end{figure}

@@

	\begin{figure}[htb]
		\newcommand{\taskA}[2][0]{\task[#1]{$A$}{#2}{4}{1}{cyan}}
		\newcommand{\taskB}[2][0]{\task[#1]{$B$}{#2}{2}{6}{cyan!50!black}}
		\newcommand{\taskC}[2][0]{\task[#1]{$C$}{#2}{8}{8}{blue!40!white}}
		\newcommand{\taskD}[2][0]{\task[#1]{$D$}{#2}{5}{4}{blue!70!white}}
		\newcommand{\taskE}[2][0]{\task[#1]{$E$}{#2}{3}{2}{blue}}
		\begin{tikzpicture}[yscale=0.6,xscale=0.2]
		\begin{scope}
		\schedule{35}{OOLCMR}{2,8,12,15,17,25,33}
		\taskB{0}
		\taskD[1]{2}
		\taskA{8}
		\taskE{12}
		\taskC{17}
		\end{scope}
		\begin{scope}[yshift=-2.75cm]
		%%		\schedule{36}{OOSCMR}{2,5,8,11,14,18,26,34}
		%%		\taskB{0}
		%%		\taskE[3]{2}
		%%		\taskA[1]{5}
		%%		\taskD{9}
		%%		\taskC{18}
		%%		\end{scope}
		\schedule{36}{OOSCMR}{2,5,8,11,15,19,27,35}
		\taskB{0}
		\taskE[3]{2}
		\taskA[1]{5}
		\taskD{10}
		\taskC{19}
		\end{scope}
		\begin{scope}[yshift=-5.5cm]
		\schedule{36}{OOMAMR}{2,8,11,14,17,25,33}
		\taskB{0}
		\taskD[1]{2}
		\taskE[1]{8}
		\taskA{12}
		\taskC{17}
		\end{scope}
		%%		\begin{scope}[yshift=+2.75cm]
		%%		\schedule{40}{OMIM}{2,8,16,24,29,33,38}
		%%		\taskB{0}
		%%		\taskC{8}
		%%		\taskD{24}
		%%		\taskA{29}
		%%		\taskE{33}
		%%		\end{scope}

		\end{tikzpicture}
		\caption{ \label{fig:staticOrderDynamicCorrectionsExample} Different static order dynamic corrections heuristic schedules for a task set of Table~\ref{tab:staticOrderDynamicCorrectionsExample} with a memory capacity of 9. The $OMIM$ order is $BCDAE$.}
	\end{figure}

	%%\begin{figure}[htb]
	%%\includegraphics[scale=0.05]{Figs/staticOrderDynamicCorrectionsSchedules}
	%%\caption{Task set and schedules where orders are precomputed based on different heuristics.}
	%%\label{fig:staticOrderDynamicCorrectionsExample}
	%%\end{figure}

@@

	\noindent Let $L=\sum_i (COMP_i + COMM_i)$. It is evident that $e_i =s_i + COMM_i$ and $e'_i =s'_i + COMP_i$. The linear program is given below.

@@

@@

		\begin{figure}[htb]
			%\begin{tabular}{c}
			\includegraphics[scale=0.5]{./results/application_properties.pdf}
			\caption{HF and CCSD tasks characteristics.}
			\label{fig:ApplicationProperties}
		\end{figure}

@@

		\begin{figure*}[htb]
			%%			\includegraphics[scale=0.5]{./results/inverse_ratio_to_optimal_batch-best.pdf}
			\includegraphics[scale=0.5]{./results/ratio_to_optimal_batch-best.pdf}
			\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
			\label{fig:best_variants_batch}
		\end{figure*}

>>>>

%
\documentclass[runningheads]{llncs} %
\usepackage{graphicx}

\usepackage[utf8]{inputenc}
%%\usepackage{amsmath}
%%\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{threeparttable}
\usepackage{graphicx}
\usepackage{color}
\usepackage{paralist}
\usepackage{framed}
\usepackage{caption}
%%\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{todonotes}
\usepackage{subfig}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{hyperref}
%%\usepackage{url}

@@

\makeatletter
\newcommand{\pushright}[1]{\ifmeasuring@#1\else\omit\hfill$\displaystyle#1$\fi\ignorespaces}
\newcommand{\pushleft}[1]{\ifmeasuring@#1\else\omit$\displaystyle#1$\hfill\fi\ignorespaces}
\makeatother

\newcommand{\scomm}{\ensuremath{{\cal S}_{\text{COMM}}}}
\newcommand{\scomp}{\ensuremath{{\cal S}_{\text{COMP}}}}

%%\newcommand{\scomm}{\ensuremath{{S}_{\text{COMM}}}}
%%\newcommand{\scomp}{\ensuremath{{S}_{\text{COMP}}}}

\newcommand{\threepart}{\textsc{3Par}\xspace}

@@

\begin{document} %
	%	\title{Contribution Title\thanks{Supported by organization x.}}
	\title{Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels}
	\titlerunning{Performance Models for Data Transfers}
	% If the article title is too long for the running head, you can set
	% an abbreviated article title here
	%
%%	\author{}
	\author{Suraj Kumar \inst{1}\and 
		Lionel Eyraud-Dubois \inst{2}\and 
		Sriram Krishnamoorthy \inst{1}} %
	\authorrunning{Kumar and Eyraud-Dubois, et al.} % First names are abbreviated in the running
%%	% head.
%%	% If there are more than two authors, 'et al.' is used.
%%	%
	\institute{Pacific Northwest National Laboratory, Richland, Washington, USA \\
		\email{\{suraj.kumar, sriram\}@pnnl.gov}
		\and
		 Inria Bordeaux -- Sud-Ouest, Université de Bordeaux, France\\
		\email{lionel.eyraud-dubois@inria.fr}} %
	\maketitle              % typeset the header of the contribution
	%
	\begin{abstract} 
%%		
		With increasing complexity of hardwares, systems with different memory nodes are ubiquitous in High Performance Computing (HPC). It is paramount to develop strategies to overlap the data transfers between memory nodes with computations in order to exploit the full potential of these systems. In this article, we consider the problem of deciding the order of data transfers between two memory nodes for a set of independent tasks with the objective to minimize the makespan. We prove that with limited memory capacity, obtaining the optimal order of data transfers is a NP-complete problem. We propose several heuristics for this problem and provide details about their favorable situations. We present an analysis of our heuristics on traces, obtained by running 2 molecular chemistry kernels, namely, Hartree–Fock (HF) and Coupled Cluster Single Double (CCSD) on 10 nodes of an HPC system. Our results show that some of our heuristics achieve significant overlap for moderate memory capacities and are very close to the lower bound of makespan.

		\keywords{Communication Scheduling  \and Memory Nodes \and Runtime Systems \and Communication-Computation Overlap \and Molecular Chemistry.}
	\end{abstract} %

@@

Certain applications such as dense linear algebra kernels have regular structure. Therefore, it is possible to associate priorities to computations, based on the task graph structure, and to use them at runtime to make the execution efficient. In irregular applications, programmers do not know the precise structure of the task graphs in advance: tasks are added recursively based on certain sentinel constraints. For such applications, the runtime system sees a set of independent tasks and schedules them on different processing units. It is extremely important for runtimes to decide the order of data transfers for these scheduled computations so as to maximize the overlap between computations and communications. This is the main topic of this article. We prove that the order of communications on two memory nodes with the objective of minimizing the makespan is a NP-Complete problem if the memory of the target node is limited. Our proof is inspired from work by~\cite{Papadimitriou:1980:FSL:322203.322213}, which applies a similar technique for 2-machine flowshop problem with bounded capacity. The main difference between both approaches is that they consider all tasks have the same occupation on the second machine and the memory occupation starts when the processing finishes on the first machine. On the contrary, our approach is designed for tasks appearing in scientific workloads whose memory requirements are highly irregular and we consider that memory is acquired before starting the data transfer on the communication resource. We propose different runtime strategies in order to maximize the overlap of computations and communications. We evaluate our strategies on the context of a cluster of homogeneous nodes. However, our approach is generic and easily adaptable to any system which operates on different memory spaces. Here are the important contributions of this article:

@@

The outline of the article is the following. Section~\ref{sec:relatedWork} describes past work on the computations with limited memory and similar problems in the literature. In section~\ref{sec:theoreticalProof}, we present an algorithm to obtain the order of data transfers when there is not any memory capacity restriction. Then, we also prove that in general data transfer problem is NP-complete. In Section~\ref{sec:heuristics}, we propose several heuristics and describe their favorable scenarios. We mainly consider three categories of heuristics: static heuristics, dynamic heuristics and static heuristics with dynamic corrections. Sections~\ref{sec:expSetting} describes our experimental setup and we evaluate our proposed strategies on two molecular chemistry kernels in Section~\ref{sec:expResults}. Our results show that static heuristics with dynamic corrections achieve good performance in most cases. We finally propose conclusions and perspectives in Section~\ref{sec:conclusion}.

@@

The problem considered in this article also can be viewed as a flow shop problem: the communication link can be seen as a processing resource, and each task needs to first be handled by the communication link and then by the computational resource. Communication and computation times of a task can thus be considered as processing times on different machines. Johnson has provided scheduling strategies for 2 and 3-machine flow shop problems with infinite memory capacity~\cite{johnson}. 2-machine flow shop problem with finite buffer has been proven NP-Complete by Papadimitriou et. al~\cite{Papadimitriou:1980:FSL:322203.322213}, in which a constraint is imposed on the number of tasks that can await execution on the second machine.

@@

@@

\noindent\textbf{Problem $DT$} : A set of tasks $ST=\{T_1,
\cdots, T_n\}$ is scheduled on a processing unit $P$ with
memory unit $M$ of capacity $C$. Input data for tasks of $ST$
reside on another memory unit $M'$. $CM_i$ is the communication time to
transfer input data from $M'$ to $M$ for task $i$ and $CP_i$
is the computation time of task $i$ on $P$. We assume that these
tasks do not produce any output data. There can be only one
communication at a time, and $P$ can only process one task at
a time. A task uses an amount of memory in  $M$ from the
start of its communication to the end of its computation.

@@

Given a schedule, \scomm($i$) and \scomp($i$) represent the
start times of task $i$ on communication and computation
resources. A schedule is feasible if for every time $t$, the
amount of memory required by all tasks such that $\scomm(i) \leq t
\leq \scomp(i) + CP_i$ is not more than the memory capacity
$C$. 
For simplicity, we assume throughout the article that tasks
require memory only to store their input data, and thus that
the amount of memory required by a task is proportional to its
communication time. Without loss of generality, we consider in
all examples of Sections~\ref{sec:theoreticalProof}
and~\ref{sec:heuristics} that the memory requirement of a task
is equal to its communication time.

%% We assume through out the article that communication time of a task is proportional to memory required by it, and follow conventional \textit{Comm Time = Latency + (Comm Volume)/Bandwidth} model.
%%	
We call a task $i$ compute intensive if $CP_i \ge CM_i$, and
communication intensive otherwise.

@@

\begin{algorithm}
	\caption{\label{alg:OrderOfExecutionInfinteMemory}Johnson's~\cite{johnson} algorithm (infinite memory case).}
	\begin{algorithmic}[1]
		\STATE Divide ready tasks in two sets $S_1$ and $S_2$. If computation time of a task $T$ is not less than its communication time, then $T$ is in $S_1$ otherwise in $S_2$.
		\STATE Sort $S_1$ in queue $Q$ by non-decreasing communication times
		\STATE Sort $S_2$ in queue $Q'$ by non-increasing computation times
		\STATE Append $Q'$ to $Q$
		\STATE $\tau_{\text{COMM}} \gets 0$ \hfill\COMMENT{Available time of communication resource}
		\STATE $\tau_{\text{COMP}} \gets 0$\hfill \COMMENT{Available time of computation resource}
		\WHILE{$Q \neq \emptyset$}
		\STATE Remove a task $T$ from beginning of $Q$ for processing
		\STATE $\scomm(T) \gets \tau_{\text{COMM}}$
		\STATE $\scomp(T) \gets max(\scomm(T) + CM_T, \tau_{\text{COMP}})$
		\STATE $\tau_{\text{COMM}} \gets \scomm(T) + CM_T$
		\STATE $\tau_{\text{COMP}} \gets \scomp(T) + CP_T$
		\ENDWHILE
	\end{algorithmic}
\end{algorithm}

We  prove optimality of Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}  differently. Our proof rely on the following lemma.

\begin{lemma}\label{lemma:swappingOfTasks}
	Swapping two contiguous tasks $A$ and $B$ in a schedule does not improve the makespan if one of the conditions is true.
	\begin{enumerate}[label=\roman*)]
		\item  $CP_A \ge CM_A, CP_B \ge CM_B, CM_A \le CM_B$
		\item $CP_A < CM_A, CP_B < CM_B, CP_A \ge CP_B$
		\item $CP_A \ge CM_A, CP_B < CM_B$
	\end{enumerate}
\end{lemma}
\begin{proof}
	Let $t_1$ and $t_2$ be the early start time on communication and computation resources just before the task $A$ starts.

	\begin{figure}[htb]
		\centering
		\includegraphics[scale=0.35]{./original_swapped_schedules-eps-converted-to.pdf}
		\caption{ \label{fig:bothSchedule} Original and Swapped Schedules.}
	\end{figure}
	We write the following constraints based on the two schedules of the Fig~\ref{fig:bothSchedule}.

	\noindent $\scomp(A) = max(t_1 + CM_A, t_2)$ \\
	\noindent $\scomp(B) = max(\scomp(A) + CP_A,  t_1 + CM_A + CM_B)$\\

	\noindent Completion time of $B$ in original Schedule = $\scomm(B) + CP_B$\\
	\noindent Completion time of $B$ in swapped Schedule,  $\scomp '(B)  =  max(t_1 + CM_B, t_2)$\\
	\noindent Completion time of $A$ in swapped Schedule, $ \scomp '(A)$ \newline
	 \hspace*{0pt}\hfill $ = max(\scomp'(B) + CP_B, t_1 + CM_B + CM_A)$

	\noindent In both schedules, early available time on communication resource after scheduling $A$ and $B$ is same. If we show that early available time on computation resource in swapped schedule after scheduling both tasks is not less than the time of original schedule, then the proof is complete. Hence our goal is to prove that,		
	$$\scomp(B) + CP_B \le \scomp'(A) + CP_A $$

%%	\begin{eqnarray*}
%%		\scomp(B) + CP_B & = & max(\scomp(A) + CP_A + CP_B,  t_1 + CM_A + CM_B + CP_B)\\
%%		& = & max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A\\
%%		&& + CM_B + CP_B) 
%%	\end{eqnarray*}
{\small
		\begin{align*}
				\scomp(B) + CP_B & =  &max(\scomp(A) + CP_A + CP_B,  t_1 + CM_A + CM_B + CP_B)\\
				& = & max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A\\
				& &+ CM_B + CP_B) 
		\end{align*}
	Case I: $CP_A \ge CM_A, CP_B \ge CM_B, CM_A \le CM_B$
	\begin{align*}
		\scomp(B) + CP_B & =  max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A \\
		&\pushright{+ CM_B + CP_B)}\\
		& \le max(t_1 + CM_A + CP_B, t_2  + CP_B, t_1  + CM_B + CP_B) + CP_A\\
		& =  max( t_1  + CM_B + CP_B, t_2  + CP_B) + CP_A \\
		& =  max(max(t_1 + CM_B, t_2) + CP_B, t_1 + CM_A + CM_B) + CP_A\\
		& =  max(\scomp'(B) + CP_B, t_1 + CM_A + CM_B) + CP_A \\
		& =  \scomp'(A) + CP_A
	\end{align*}
	Case II: $CP_A < CM_A, CP_B < CM_B, CP_A \ge CP_B$
	\begin{align*}
		\scomp(B) + CP_B & =  max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A \\
		& \pushright{+ CM_B + CP_B)}\\
		& \le  max(t_1 + CM_A + CP_B, t_2+CP_B, t_1 + CM_A + CM_B) + CP_A\\
		& =  max(t_1 + CM_A + CM_B, t_2+ CP_B) + CP_A \\
		& =  max(t_1 + CM_B + CP_B, t_2 + CP_B, t_1 + CM(A) + CM_B) + CP_A \\
		& =  max(max(t_1 + CM_B, t_2) + CP_B, t_1 + CM_A + CM_B) + CP_A \\
		& =  max(\scomp'(B) + CP_B, t_1 + CM_A +CM_B) + CP_A \\
		& =  \scomp'(A) + CP_A
	\end{align*}
	Case III: $CP_A \ge CM_A, CP_B < CM_B$
%%	\begin{eqnarray*}
%%		\scomp(B) + CP_B & = & max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A + CM_B + CP_B)\\
%%		& \le & max(t_1 + CM_A + CP_B, t_2 + CP_B, t_1 + CM_B + CP_B) + CP_A\\
%%		& \le & max(t_1 + CM_A + CM_B, t_2 + CP_B, t_1 + CM_B + CP_B) + CP_A \\
%%		& = & max(max(t_1 + CM_B, t_2) + CP_B, t_1 + CM_A + CM_B) + CP_A \\
%%		& = & max(\scomp'(B) + CP_B, t_1 + CM_A +CM_B) + CP_A \\
%%		& = & \scomp'(A) + CP_A
%%	\end{eqnarray*}
	\begin{align*}
	\scomp(B) + CP_B & =  max(t_1 + CM_A + CP_A + CP_B, t_2 + CP_A + CP_B, t_1 + CM_A\\ 
	&\pushright{+ CM_B + CP_B)}\\
	& \le  max(t_1 + CM_A + CP_B, t_2 + CP_B, t_1 + CM_B + CP_B) + CP_A\\
	& \le  max(t_1 + CM_A + CM_B, t_2 + CP_B, t_1 + CM_B + CP_B) + CP_A \\
	& =  max(max(t_1 + CM_B, t_2) + CP_B, t_1 + CM_A + CM_B) + CP_A \\
	& =  max(\scomp'(B) + CP_B, t_1 + CM_A +CM_B) + CP_A \\
	& =  \scomp'(A) + CP_A
\end{align*}
}

\end{proof}

\begin{theorem}
	Scheduled constructed by Algorithm~\ref{alg:OrderOfExecutionInfinteMemory} achieves optimal makespan.
\end{theorem}

\begin{proof}

	Let $O$ be an optimal schedule. We assume that $O$ is a permuation schedule, If it is not the case, we make the order of computations same as the order of communications without increasing the makespan.  Suppose two tasks have opposite order on both resources then we position the second task just before the first task on the computation resource. It is evident that this change does not alter the optimal  makespan, we repeat this procedure until order of communications and computations is same in $O$.

	Let $S$ be the  schedule obtained from Algorithm~\ref{alg:OrderOfExecutionInfinteMemory}. We prove the theorem by converting $S$ to $O$ and showing that at each step makespan of intermediate schedule is not less than the original makespan. We rely on Lemma~\ref{lemma:swappingOfTasks} to convert $S$ to $O$.

	We traverse schedule $O$ from left to right and for each $ith$ task in sequence, we apply Lemma~\ref{lemma:swappingOfTasks} repetitively until order of task in the swapped schedule is same. It is obvious that after moving the $ith$ task at the beginning remaining schedule (schedule after $ith$ task) still satisfies one of the conditions of Lemma~\ref{lemma:swappingOfTasks}.

	Let the final swapped schedule is $S_{final}$. From Lemma~\ref{lemma:swappingOfTasks}, $makespan(S_{final})$ $ \ge $ $makesapn(S)$. From the construction, $makespan(S_{final})$ $ \le$ $ makesapn(O)$. As $O$ is an optimal schedule, hence $makespan(S) = makesapn(O)$. This completes our proof.
\end{proof}

\subsection{Finite Memory}

@@

	As mentioned previously, we consider memory requirement of a task is equal to its communication time. If it is not the case, we can adjust $C$ such that at any point in a schedule at max one $K_i$ and three $A_i$ tasks can be active.

@@

This theorem shows that adding a memory constraint to our
problem makes it more difficult. One additional difficulty
compared to infinite memory capacity 2-machine flowshop~\cite{johnson} is that
it may not be optimal to consider the same ordering on both
machines:

@@

%%\begin{figure}[htb]
%%	
%%	\includegraphics[scale=0.05]{./staticOrderSchedules}
%%			\caption{Task set and schedules where orders are precomputed based on different heuristics.}
%%	\label{fig:staticOrderExample}
%%\end{figure}

@@

\begin{figure}[htb]
	\begin{center}
	\newcommand{\taskA}[2][0]{\task[#1]{$A$}{#2}{4}{1}{cyan}}
	\newcommand{\taskB}[2][0]{\task[#1]{$B$}{#2}{2}{6}{cyan!50!black}}
	\newcommand{\taskC}[2][0]{\task[#1]{$C$}{#2}{8}{8}{blue!40!white}}
	\newcommand{\taskD}[2][0]{\task[#1]{$D$}{#2}{5}{4}{blue!70!white}}
	\newcommand{\taskE}[2][0]{\task[#1]{$E$}{#2}{3}{2}{blue}}
	\begin{tikzpicture}[yscale=0.6,xscale=0.2]
	\begin{scope}
	\schedule{35}{OOLCMR}{2,8,12,15,17,25,33}
	\taskB{0}
	\taskD[1]{2}
	\taskA{8}
	\taskE{12}
	\taskC{17}
	\end{scope}
	\begin{scope}[yshift=-3cm]
	%%		\schedule{36}{OOSCMR}{2,5,8,11,14,18,26,34}
	%%		\taskB{0}
	%%		\taskE[3]{2}
	%%		\taskA[1]{5}
	%%		\taskD{9}
	%%		\taskC{18}
	%%		\end{scope}
	\schedule{36}{OOSCMR}{2,5,8,11,15,19,27,35}
	\taskB{0}
	\taskE[3]{2}
	\taskA[1]{5}
	\taskD{10}
	\taskC{19}
	\end{scope}
	\begin{scope}[yshift=-6cm]
	\schedule{36}{OOMAMR}{2,8,11,14,17,25,33}
	\taskB{0}
	\taskD[1]{2}
	\taskE[1]{8}
	\taskA{12}
	\taskC{17}
	\end{scope}
	%%		\begin{scope}[yshift=+2.75cm]
	%%		\schedule{40}{OMIM}{2,8,16,24,29,33,38}
	%%		\taskB{0}
	%%		\taskC{8}
	%%		\taskD{24}
	%%		\taskA{29}
	%%		\taskE{33}
	%%		\end{scope}

	\end{tikzpicture}
	\caption{ \label{fig:staticOrderDynamicCorrectionsExample} Different static order dynamic corrections heuristic schedules for a task set of Table~\ref{tab:staticOrderDynamicCorrectionsExample} with a memory capacity of 9. The $OMIM$ order is $BCDAE$.}
	\end{center}
\end{figure}

%%\begin{figure}[htb]
%%\includegraphics[scale=0.05]{./staticOrderDynamicCorrectionsSchedules}
%%\caption{Task set and schedules where orders are precomputed based on different heuristics.}
%%\label{fig:staticOrderDynamicCorrectionsExample}
%%\end{figure}

@@

\noindent Let $L=\sum_i (CP_i + CM_i)$. It is evident that $e_i =s_i + CM_i$ and $e'_i =s'_i + CP_i$. The linear program is given below.

@@

		\begin{figure}[htb]
		\begin{center}
			\includegraphics[scale=0.5]{./application_properties.pdf}
			\caption{HF and CCSD tasks characteristics.}
			\label{fig:ApplicationProperties}
		\end{center}
		\end{figure}

@@

@@
